---
title: "Minimal pin example"
author: "LA"
date: "2023-10-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Deploy pin

```{r}
library(rsconnect)
library(pin)
library(tidyverse)

Sys.setenv(CONNECT_API_KEY = "<redacted>")
Sys.setenv(CONNECT_SERVER = "<redacted>")

cars_data <- cars

board <- board_connect(auth = "envvar")
board %>% pin_write(cars_data, "pin_cars_min", type = "rds")
```


Alternatively, [`usethis`](https://usethis.r-lib.org/) has a function for creating and editing the .Renviron file: 

```r
library(usethis)
usethis::edit_r_environ()
```

Add the variables to that file in the format `variable_name = "variable_value"` and save it. Restart the session so the new environment variables will be loaded with `ctrl shift f10` or through the RStudio IDE through the **Session** dropdown and selecting **Restart R**. 

It should look like this: 

```
CONNECT_API_KEY=<redacted>
```

## Read pin 

```{r}
## Read pin 

library(rsconnect)
library(pins)
library(tidyverse)

#Check our environment variables
# usethis::edit_r_environ()

board <- board_connect(auth = "envvar")

cars_data_back <-board %>% pin_read("lisa.anders/pin_cars_min")

```


## Reading pin from deployed content 

See the Connect User Guide for adding the variables using the UI to deployed content: <https://docs.posit.co/connect/user/content-settings/index.html#content-vars>

