---
title: "Environment Variables"
author: "LA"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Environment Variables 

```{r}
print(Sys.getenv("ENV_VAR"))
```


### How does this work? 

Variables are being saved to the user level .Renviron config file when working on the file in Workbench

For this project the following variables are being saved in the .Renviron file (credentials are stripped for security), as well as added to Connect as environment variables for pins content: 

 - CONNECT_API_KEY=**REDACTED**
 - CONNECT_SERVER=**REDACTED**
 - OWNER_GUID=**REDACTED**

<details>
  <summary>Relevant reading:</summary>

When working in a more complex environment structure where separate project, site, and user environments are being used [this support article has useful information](https://support.rstudio.com/hc/en-us/articles/360047157094-Managing-R-with-Rprofile-Renviron-Rprofile-site-Renviron-site-rsession-conf-and-repos-conf) with a [deeper dive into R's startup here](https://rviews.rstudio.com/2017/04/19/r-for-enterprise-understanding-r-s-startup/).

</details>

#### One-off

Set an environment variable: 

```{r}
Sys.setenv(CONNECT_API_KEY = "<redacted>")
```


Recall an environment variable: 

```{r}
Sys.getenv("CONNECT_API_KEY")
```

#### Persistence 

[`usethis`](https://usethis.r-lib.org/) has a function for creating and editing the .Renviron file: 

```r
library(usethis)
usethis::edit_r_environ()
```

Add the variables to that file in the format `variable_name = "variable_value"` and save it. Restart the session so the new environment variables will be loaded with `ctrl shift f10` or through the RStudio IDE through the **Session** dropdown and selecting **Restart R**. 

It should look like this: 

```
CONNECT_API_KEY=<redacted>
```

#### Adding environment variables to deployed content

See the Connect User Guide for adding the variables using the UI to deployed content: <https://docs.posit.co/connect/user/content-settings/index.html#content-vars>


Write the manifest: 

```r
library(rsconnect) 
rsconnect::writeManifest(appDir="R/env_var")
```

Now you should be good to go! 


