---
title: "Pin mtcars"
output: html_document
---

## Purpose

This script pulls demo information from mtcars and pins it so the data set is usable by others. 

- Pins to: <https://colorado.posit.co/rsc/connect/#/apps/1d002e9f-1922-4fa7-bfbd-b3262dcde0ad/access> 

- Access the script, and schedule it, at: <https://colorado.posit.co/rsc/connect/#/apps/3dae5785-607d-451f-8551-820d5a07ae1d/access> 

- The pinned data is being consumed in an app: <https://colorado.posit.co/rsc/connect/#/apps/a0aa6140-686c-4bc1-bb51-5596e5e99436/access> 

```{r global, echo=FALSE, message=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyverse)
library(stringr)
library(readr)
library(pins)
library(rsconnect)
library(usethis)

#Check our environment variables
# usethis::edit_r_environ()

```

```{r main, echo=FALSE, message=FALSE}
library(dplyr)
library(tidyverse)
library(stringr)
library(readr)
library(pins)
library(rsconnect)
library(usethis)

#Pull data
summary(cars)
cars_data <- cars

#Pin data to board
board <- board_connect(auth = "envvar")
board %>% pin_write(cars_data, "cars_dataset", type = "rds")


```
## Conclusion

If you're reading this, it worked!

This document will be run on a schedule in the Connect environment, to provide updated data.  

## Source

The code for this page lives [in github](https://github.com/leesahanders/Shiny_Geyser_App)

## How to use this code 

Read it back with: 

```{r}

board <- board_connect(auth = "envvar")

cars_data_back <-board %>% pin_read("lisa.anders/cars_dataset")

```

